---
title: "Cal/Val Summary"
author: "Luke Winslow"
date: "March 22, 2016"
output: html_document
params:
  out_df: !r data.frame()
  run_message: !r "default message"
---

Run description: `r params$run_message`


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(lubridate)
library(glmtools)
library(mda.lakes)
library(plyr)

out_df = params$out_df

#out_df = read.table('c:/WiLMA/results/2016-03-21_NLDAS.tsv', header=TRUE, sep='\t', as.is=TRUE)
Sys.setenv(tz='GMT')

out_df$DateTime   = as.POSIXct(out_df$DateTime)
out_df$month      = month(out_df$DateTime)
out_df$modLessObs = out_df$Modeled_temp - out_df$Observed_temp
out_df$Depth_1   = floor(out_df$Depth/1)*1

epi = calc_mod_obs_metric(out_df, 'epi.temperature')

hypo = calc_mod_obs_metric(out_df, 'hypo.temperature')

metric_calc_bylake = function(df){
  data.frame(rmse=sqrt(mean((df$mod - df$obs)^2, na.rm=TRUE)), bias=mean(df$mod - df$obs, na.rm=TRUE), ndates=nrow(df))
}


epi_bylake = ddply(epi, 'site_id', metric_calc_bylake)
hypo_bylake = ddply(hypo, 'site_id', metric_calc_bylake)

epi_bylake = subset(epi_bylake, ndates >=10)
hypo_bylake = subset(hypo_bylake, ndates >=10)

```

#Run and code info
Specific mda.lakes version on github [link](`r paste0('https://github.com/USGS-R/mda.lakes/tree/', system('git rev-parse HEAD', intern = TRUE))`)

Package | Version
--------|-------
mda.lakes      | `r packageVersion('mda.lakes')`
lakeattributes | `r packageVersion('lakeattributes')`
GLMr           | `r packageVersion('GLMr')`
glmtools       | `r packageVersion('glmtools')`


#Classic, general stats:

Statistic | Value
----------|-------
n obs     | `r nrow(na.omit(out_df)) `
n lakes   | `r length(unique(out_df$site_id)) `
RMSE      | `r sqrt(mean((out_df$modLessObs)^2, na.rm=TRUE)) `
Mean error| `r mean(out_df$modLessObs, na.rm=TRUE)`

# Epi and Hypo lake-specific RMSE

These are RMSE calculated for each lake, then the 50th and 95th percentile of those per-lake values 
are presented. 

Layer | 50% | 95% 
------|-----|-----
Epi | `r quantile(epi_bylake$rmse, probs=0.5)` | `r quantile(epi_bylake$rmse, probs=0.95)`
Hypo RMSE | `r quantile(hypo_bylake$rmse, probs=0.5)` | `r quantile(hypo_bylake$rmse, probs=0.95)` 

#Epi and Hypo lake-specific Bias stats

Layer | 2.5% | 50% | 97.5 
------|-----|-----|-------
Epi Bias  | `r quantile(epi_bylake$bias, probs=0.025)` | `r quantile(epi_bylake$bias, probs=0.5)` | `r quantile(epi_bylake$bias, probs=0.975)` 
Hypo Bias | `r quantile(hypo_bylake$bias, probs=0.025)` | `r quantile(hypo_bylake$bias, probs=0.5)` | `r quantile(hypo_bylake$bias, probs=0.975)` 


#Overall observed vs model:
```{r, echo=FALSE, fig.width=5, fig.height=7, warning=FALSE}

par(mfrow=c(3,1), mar=c(1,4,0,1), oma=c(3,0,1,0))

plot(out_df$Observed_temp, out_df$Modeled_temp, col=rgb(0, 0, 0, 0.1), pch=16, xlim=c(0,30), ylim=c(0,30), xaxt='n', ylab='Modeled Temp')

abline(0, 1)


plot(epi$obs, epi$mod, col=rgb(0, 0, 0, 0.1), pch=16, xlim=c(0,30), ylim=c(0,30), ylab='Modeled Epi', xaxt='n')
abline(0, 1)


plot(hypo$obs, hypo$mod, col=rgb(0, 0, 0, 0.1), pch=16, xlim=c(0,30), ylim=c(0,30), ylab='Modeled Hypo', xlab='Observed')
abline(0, 1)

```

Statistic | RMSE  | Avg Resid
----------|-------|------
All Temp  | `r sqrt(mean((out_df$modLessObs)^2, na.rm=TRUE)) ` | `r mean(out_df$modLessObs, na.rm=TRUE)`
Epi RMSE  | `r sqrt(mean((epi$mod - epi$obs)^2, na.rm=TRUE))` | `r mean(epi$mod - epi$obs, na.rm=TRUE)` 
Hypo RMSE | `r sqrt(mean((hypo$mod - hypo$obs)^2, na.rm=TRUE))` | `r mean(hypo$mod - hypo$obs, na.rm=TRUE)`





#Residuals across depth:

```{r, echo=FALSE}
boxplot(modLessObs~Depth_1, out_df, ylab="Model - Observation", xlab='Depth (m)', ylim=c(-10, 10))
abline(h=0)
```


#Seasonality of residuals:

```{r, echo=FALSE}
boxplot(modLessObs~month, out_df, ylab="Model - Observation", xlab='Month', ylim=c(-10, 10))
abline(h=0)

```


```{r, echo=FALSE}

library(leaflet)
library(plyr)
library(lakeattributes)

lake_stats = ddply(out_df, 'site_id', function(df){
  
  rmse = sqrt(mean((df$Observed_temp - df$Modeled_temp)^2, na.rm=TRUE))
  bias = mean(df$Modeled_temp - df$Observed_temp, na.rm=TRUE)
  n = nrow(df)
  data.frame(rmse, bias, n)
  
})

data(canopy)

lake_stats = merge(lake_stats, lakeattributes::location, by='site_id')
lake_stats = merge(lake_stats, lakeattributes::area, by='site_id')
lake_stats = merge(lake_stats, lakeattributes::zmax, by='site_id')
lake_stats$secchi = 1.7/get_kd_avg(lake_stats$site_id)$kd_avg
lake_stats = merge(lake_stats, canopy, by='site_id')

```

#
```{r, echo=FALSE}

par(mfrow=c(2,1), mar=c(0,4,1,1), oma=c(4,0,0,0))
plot((lake_stats$area_m2), lake_stats$bias, xlab='Lake area m^2', ylab='by-obs Bias', xaxt='n', log='x')
plot((lake_stats$area_m2), lake_stats$rmse, xlab='Lake area m^2', ylab='by-obs RMSE', log='x')
mtext(text='Log10(lake area m^2)', side=1, line=2)

```

```{r, echo=FALSE}
par(mfrow=c(2,1), mar=c(0,4,1,1), oma=c(4,0,0,0))
plot(lake_stats$secchi, lake_stats$bias, xlab='Secchi(m)', ylab='by-obs Bias', xaxt='n')
plot(lake_stats$secchi, lake_stats$rmse, xlab='Secchi(m)', ylab='by-obs RMSE')
mtext(text='Secchi(m)', side=1, line=2)
```

```{r, echo=FALSE}
par(mfrow=c(2,1), mar=c(0,4,1,1), oma=c(4,0,0,0))
plot(lake_stats$zmax_m, lake_stats$bias, log='x', xlab='Log(zmax)', ylab='by-obs Bias', xaxt='n')
plot(lake_stats$zmax_m, lake_stats$rmse, log='x', xlab='Log(zmax)', ylab='by-obs RMSE')
mtext(text='zmax', side=1, line=2)
# 
# par(mfrow=c(2,1))
# boxplot(bias~canopy_m, lake_stats)
# abline(h=0)
# height = as.numeric(names(tmp))
# barplot(height~tmp)


```

## Map of Bias

```{r, echo=FALSE}

m = leaflet() %>% addTiles() %>% 
  addCircleMarkers(lng=lake_stats$lon, lat=lake_stats$lat, radius=4, stroke=TRUE, weight=1, 
                   fillColor=colorNumeric(c('Blue', 'White', "Red"), (lake_stats$bias))((lake_stats$bias)),
                   fillOpacity=1, popup=paste0('Bias: ', lake_stats$bias, '<br>RMSE:', lake_stats$rmse, '<br>N:', 
                                               lake_stats$n, '<br>ID:', lake_stats$site_id))

m


```

## Map of RMSE

```{r, echo=FALSE}

m = leaflet() %>% addTiles() %>% 
  addCircleMarkers(lng=lake_stats$lon, lat=lake_stats$lat, radius=4, stroke=TRUE, weight=1, 
                   fillColor=colorNumeric(c('White', "Red"), (lake_stats$rmse))((lake_stats$rmse)),
                   fillOpacity=1, popup=paste0('Bias: ', lake_stats$bias, '<br>RMSE:', lake_stats$rmse, '<br>N:', 
                                               lake_stats$n, '<br>ID:', lake_stats$site_id))

m


```
